\huge A Usability Evaluation of Tor Launcher

### 2016-10-28 pets2017-paper/pets2017-paper.tex
write the design procedure subsection, refer to placeholder image of redesigned interface screens

\subsection{Procedure} 
{\color {blue}
We had 1 security researcher, 2 usable security researchers, and 1 UI designer. All the researchers watched the videos, that they have not seen. The researchers talked about the observations from the formative study, then discussed the design principles that we wanted to follow, what the goals of this re-design was, and then and brainstormed ideas on how to make things better.  We caught up the designer and summarized what had happened, giving him access to the videos, interviews, and resources. We went back and forth on iteratively mocking up wireframes and clickable prototypes until we found one that we thought might be a good shot. A goal of this was to discover some changes to push to the current interface.  
}

>>>>

\subsection{Procedure} 
Three researchers agreed on security and usability design principles. 
We then rewatched screen capture videos and read interview transcirptions to brainstorm design changes. We provided the security and usability design principles, screen capture videos, interview transcriptions, and our suggested changes to a user interface designer, who iteratively redesigned the interface with our feedback and user interface best practices in mind. Figure~\ref{fig:new-interface} shows our redesign of the interface.

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{placeholder-fullpage.pdf}
\caption{
A redesigned version of the Tor Browser 5.0.3. Tor Launcher GUI. 
}
\label{fig:new-interface}
\end{figure*}
